Multi-line Intensity Mapping

### 2019-06-11 paper/ms.tex
Update affil

\newcommand{\penn}{Department of Physics \& Astronomy, University of
Pennsylvania, 209 South 33rd St., Philadelphia, PA 19104, USA}

@@

\email{abeane@sas.upenn.edu}

\author{Angus Beane}
\affil{\penn}

>>>>

\newcommand{\penn}{Department of Physics \& Astronomy, University of
Pennsylvania, 209 South 33rd Street, Philadelphia, PA 19104, USA}
\newcommand{\harvard}{Center for Astrophysics {\normalfont |} Harvard \& Smithsonian, 60
Garden Street, Cambridge, MA 02138, USA}

@@

\correspondingauthor{Angus Beane}
\email{abeane@sas.upenn.edu}

\author{Angus Beane}
\affil{\harvard}
\affil{\penn}
